---
title: "Data visualisation"
author: "O Steve Goa"
date: "4/11/2019"
output: html_document
---

```{r}
library(ggplot2)
```
```{r}
library(tidyverse)
```

Using mpg as a data frame
```{r, echo=TRUE}
head(mpg)
```

```{r, echo=TRUE}
data <- data.frame(mpg)
```


Shape and color of a dotted graph
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color = "blue")
```

Graph and geometric objects
```{r, echo=TRUE}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point() + 
  geom_smooth(se = FALSE)
```

Show legend code

```{r, echo=TRUE}
show.legend = FALSE
```

Recreating the R code necessary to generate the graphs as seen in the excercises from chapter 3
Requires gridExtra

```{r, echo=TRUE}
library(gridExtra)
```

```{r, echo=TRUE}
plot1 <- qplot(1)
plot2 <- qplot(1)
grid.arrange(plot1, plot2, ncol=2)
```




```{r, echo=TRUE}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point() + 
  geom_smooth()
```

```{r, echo=TRUE}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point(mapping = aes(color = class)) + 
  geom_smooth()
  
```


Requires Library Cowplot

```{r}
library(cowplot)
```

```{r, echo=TRUE}
data1 <- ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point(mapping = aes(color = class)) + 
  geom_smooth() + theme_bw()

data2 <- ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point(mapping = aes(color = class)) + 
  geom_smooth() + theme_bw() +
  theme(legend.position = c(0.8, 0.8))

plot_grid(data1, data2, labels = "AUTO")
```



Jitter amount: The geom_count()
```{r, echo=TRUE}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_point(mapping = aes(x = displ, y = hwy), position = "jitter")
```

Requires the map library
```{r}
library(maps)
```

coord_quickmap() and coord_map() are identical.
However coord_map() requires a package called "mapproj:

Example of coord_quickmap():
```{r, echo=TRUE}
nz <- map_data("nz")

ggplot(nz, aes(long, lat, group = group)) +
  geom_polygon(fill = "gray", colour = "red")

ggplot(nz, aes(long, lat, group = group)) +
  geom_polygon(fill = "gray", colour = "blue") +
  coord_map()
```

```{r}
library(mapproj)
```

libr
example of coord_map() 
```{r, echo=TRUE}
nz <- map_data("nz")

ggplot(nz, aes(long, lat, group = group)) +
  geom_polygon(fill = "gray", colour = "red")

ggplot(nz, aes(long, lat, group = group)) +
  geom_polygon(fill = "gray", colour = "blue") +
  coord_map()
```




Abline is useful for linear regression. It races a straight line through the plot.
```{r, echo=TRUE}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() + 
  geom_abline() +
  coord_fixed()
```

